Motivating Exploration in Reinforcement Learning

### 2020-04-16 paper/main.tex
related work

\section{Related Work}
Someone write this pls

>>>>

\section{Related Work}
Our artificial agent is a model-free, on-policy reinforcement learning algorithm that leverages Advantage Actor Critic (A2C) methods, entropy-based exploration methods, and curiosity-driven exploration methods. Our artificial agent uses combination(s) of these methods to learn how to navigate different OpenAI Gym (cite?) environments to maximize cumulative rewards.

Actor Critic methods have been successfully applied to a variety of reinforcement learning problems, with Advantage Actor Critic methods also being used after their introduction in 2016 through Schulman et al.’s work, High Dimensional Continuous Control Using Generalized Advantage Estimation, done at the University of California, Berkeley. Schulman et al.’s work presents the Advantage Actor Critic method that our artificial agent primarily leverages to learn how to maximize cumulative rewards in a variety of environments. Schulman et al. address two main challenges faced by policy gradient methods in reinforcement learning, namely the large number of samples usually required and the difficulty of gaining consistent improvement with nonstationarity of the data [cite].

Curiosity-driven exploration enhancements to A2C methods have also recently been applied to a set of reinforcement learning algorithms after their introduction in 2017 through Pathak et al.’s work, Curiosity-driven Exploration by Self-supervised Prediction, which was also done at the University of California, Berkeley. Pathak et al.’s work presents the curiosity-driven exploration method that our artificial agent uses, namely the Intrinsic Curiosity Module (ICM). Pathak et al.’s work addresses a challenge faced in learning when extrinsic rewards for the agent are extremely sparse through curiosity as the error in an agent’s ability to to predict the consequence of its own actions [cite]. Their proposed ICM notably ignores the aspects of the environment that do not affect the agent, as well as being able to scale to high-dimensional continuous state spaces such as images, and bypasses the difficulties of directly predicting pixels [cite].

Attention based enhancements to deep learning algorithms have also been used to solve reinforcement learning problems more efficiently. Reizinger et al.’s work, Attention-Based Curiosity-Driven Exploration In Deep Reinforcement Learning, done at the Budapest University of Technology and Economics, introduces an attention-based enhancement to A2C [cite].
